\thesistitle

### 2019-08-22 sections/results.tex
New return value table

\subsection{Return Value}
Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system.

\begin{table}[H]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textit{\textbf{Return Value}} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Maintainability}}\\\textit{\textbf{Score}}\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Number of}}\\\textit{\textbf{Refactorings}}\end{tabular} \\ \midrule
Return & 0.20 & 421 \\
Void & 0.19 & 2052 \\
Declare & 0.03 & 1318 \\
\rowcolor[HTML]{FFCCC9}
Assign & -1.29 & 3 \\ \bottomrule
\end{tabular}
\caption{Maintainability scores for different return values}
\label{tab:return}
\end{table}

>>>>

\subsection{Return Value}
Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system (categories are explained in Section~\ref{sec:refreturn}).

\begin{table}[H]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textit{\textbf{Return Value}} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Maintainability}}\\\textit{\textbf{Score}}\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Number of}}\\\textit{\textbf{Refactorings}}\end{tabular} \\ \midrule
Return & 0.19 & 1,571 \\
Declare & 0.15 & 5,177 \\
\rowcolor[HTML]{FFCCC9}
Assign & 0.12 & 14 \\
Void & -0.18 & 5,921 \\
\bottomrule
\end{tabular}
\caption{Maintainability scores for different methods of handling returned data from the call to the extracted method.}
\label{tab:return}
\end{table}
